
\begin{appendix}
    \renewcommand{\chaptername}{附录 \Alph{chapter}}
    \renewcommand{\thesection}{\Alph{chapter}.\arabic{section}}
    \renewcommand{\thesubsection}{\Alph{chapter}.\arabic{section}.\arabic{subsection}}
    \renewcommand{\thesubsubsection}{\arabic{subsubsection}.}
    \renewcommand{\thetable}{\Alph{chapter}-\arabic{table}}
    \renewcommand{\theequation}{\Alph{chapter}-\arabic{equation}}
    \renewcommand{\thefigure}{\Alph{chapter}-\arabic{figure}}
\end{appendix}

\chapter{附录标题}

加油! 终于到最后一个部分了!

\section{附录中的图形、表格、公式}


附录中的公式(\ref{equ:Call})和(\ref{equ:Put})分别为:
\begin{equation}\label{equ:Call}
  c=S_0N(d_1)-X e^{-r T}N(d_2)
\end{equation}
和
\begin{equation}\label{equ:Put}
  p=X e^{-r T}N(-d_2)-S_0N(-d_1),
\end{equation}


\section{R代码}

- 线性回归

```{r eval=FALSE, echo=TRUE}
par(mar = c(4, 4, 1, .1))
fit = lm(dist ~ 1 + speed, data = cars)
plot(cars, pch = 19, col = 'blue', las = 1)
abline(fit, lwd = 2)
```
- ggplot2

```{r eval=FALSE, echo=TRUE}
par(mar = c(4, 4, 1, .1))
fit = lm(dist ~ 1 + speed, data = cars)
plot(cars, pch = 19, col = 'blue', las = 1)
abline(fit, lwd = 2)
```

\section{Python代码}

```{python, eval=FALSE, , echo=TRUE, fig.width = 6, out.width = "75%", fig.cap="Python Figure"}
import matplotlib.pyplot as plt
import numpy as np
x = np.arange(0.0, 6.0, 0.01)
plt.plot(x, [x**2 for x in x])
plt.show()
```

